The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
Comments upto Sec3.2 addressed, except two

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Give parameter values. Set
             minor ticks.}
\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use  thicker line width for the actual histogram.  Change legend to say  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the actual equation.  Also, why are two of the horizontal lines in the bottom panel solid and one dashed?  What decides the style for eachline?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
\arun{Done. But I refer to the equations in the caption instead of the legend.}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0$, we fit
parametric models to the histograms of photometric redshifts in order
to assign values of overdensity.  We choose our bins to be $0.05$ wide
starting from $z=0.3$, where the bin width is selected to be somewhat
larger than the photometric redshift error but narrow enough that we
can still identify rather than averaging over real cosmological
structures.  We neglect the lowest
redshifts which have negligible cosmological volume and where the
galaxy population tends to be intrinsically bright and large enough
that a non-negligible fraction is lost due to the cuts we impose
(Sec.~\ref{S:data}).

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$). \rachel{What
       redshift range?}}
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of absolute magnitude $M_I$ for various
     flux-limited samples are plotted together. The vertical line
     corresponds to our luminosity cut of $-20.8$, brighter than which
     the $m_\text{F814W}<23.5$ sample includes $>95.3$ per cent of the
     galaxies in the $m_\text{F814W}<25.2$ sample.
   \rachel{Is this plot and the numbers in the caption for
     $0.8<z<0.85$ only?  This is currently implied by the text.  If
     that is true, then please fix the figure and caption to say
     this.  If that is wrong, then please fix the text.}}
   \label{fig:MIhist}
 \end{figure}

@@

There is one subtlety in our method used for estimating
completeness. We have used the full $m_\text{F814W}\le23.5$ sample
for identifying
overdensities and for the completeness calculations that motivated our
definitions of volume-limited samples. (\rachel{Do the numbers in the
  table include the full sample or just the subsample with postage stamps?}) However, in the rest of this
paper, we analyse only those galaxies for which there are postage stamp
images used to create weak lensing simulations, in part because this is the
sample for which fits to \sersic\ profiles were carried out, which is a
requirement for our morphology analysis.  
12 per cent of the galaxies that pass our cuts do not have an
associated postage stamp image.
Postage stamps may not exist because, given the size of the galaxy,
the size of the postage stamp we want to draw around it (including
some blank space) intersects the edge of the CCD.
If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
It is commonly the case that  galaxies that are nearby and
intrinsically very bright do not have postage stamps associated with
them, an effect that is dominant at lower redshifts (and is part of
our reason for excluding $z<0.3$). 
Our completeness calculation is done at high redshifts, and thus we
believe that our conclusions are not affected by this bias.

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} \&~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{Change $x$ axis label to ``Photometric redshift ($z$)''.  Use  thicker line width for the actual histogram.  Change legend to say  ``$p_1(z)$ (Eq. 1)'' and ``$p_2(z)$ (Eq. 2)'' rather than giving the actual equation.  Also, why are two of the horizontal lines in the bottom panel solid and one dashed?  What decides the style for eachline?  Finally, I think it makes sense to plot $\delta$ rather than $1+\delta$.}}
\arun{Done. But I refer to the equations in the caption instead of the legend.}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0(1.25)$, we fit
parametric models to the histograms of photometric redshifts in order
to assign values of overdensity.  We choose our bins to be $0.05$ wide
starting from $z=0.3$, where the bin width is selected to be somewhat
larger than the photometric redshift error but narrow enough that we
can still identify rather than averaging over real cosmological
structures.  We neglect the lowest
redshifts which have negligible cosmological volume and where the
galaxy population tends to be intrinsically bright and large enough
that a non-negligible fraction is lost due to the cuts we impose
(Sec.~\ref{S:data}).

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3 - 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
     The green vertical dotted line represents our luminosity cut. \rachel{What redshift range?}\arun{addressed.}} 
   \label{fig:2Dhist}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{MAG_histograms}
   \caption{Distribution of absolute magnitude $M_I$ for various
     flux-limited samples in the redshift range $[0.80 - 0.85]$ are plotted together. The vertical line
     corresponds to our luminosity cut of $-20.8$, brighter than which
     the $m_\text{F814W}<23.5$ sample includes $>95.3$ per cent of the
     galaxies in the $m_\text{F814W}<25.2$ sample.
   \rachel{Is this plot and the numbers in the caption for
     $0.8<z<0.85$ only?  This is currently implied by the text.  If
     that is true, then please fix the figure and caption to say
     this.  If that is wrong, then please fix the text.} \arun{Text is correct. Caption fixed.}}
   \label{fig:MIhist}
 \end{figure}

@@

There is one subtlety in our method used for estimating
completeness. We have used the full $m_\text{F814W}\le23.5$ sample
for identifying
overdensities and for the completeness calculations that motivated our
definitions of volume-limited samples. (\rachel{Do the numbers in the
  table include the full sample or just the subsample with postage stamps?} \arun{The subsample alone. The only place where the full sample is used is Fig. 3. The following sentence is corrected to say that.}) However, everywhere else in the paper, we consider only those galaxies for which there are postage stamp
images used to create weak lensing simulations, in part because this is the
sample for which fits to \sersic\ profiles were carried out, which is a
requirement for our morphology analysis.  
12 per cent of the galaxies that pass our cuts do not have an
associated postage stamp image.
Postage stamps may not exist because, given the size of the galaxy,
the size of the postage stamp we want to draw around it (including
some blank space) intersects the edge of the CCD.
If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
It is commonly the case that  galaxies that are nearby and
intrinsically very bright do not have postage stamps associated with
them, an effect that is dominant at lower redshifts (and is part of
our reason for excluding $z<0.3$). 
Our completeness calculation is done at high redshifts, and thus we
believe that our conclusions are not affected by this bias.
